A theoretical analysis of the Keep Network random beacon using agent based modeling \\ \thanks{Identify applicable funding agency here. If none, delete this.}

### 2019-10-21 Mesa Simulations/Conference-LaTeX-template_7-9-18 2/paper.tex
added results for multi-run linear

\subsection{How could node failures affect system behavior?}
Nodes may go offline or fail entireley. Since their participation in groups is critical to the 
success of the threshold relay, it is important to understand the impact of various levels
of failure on group characteristics. In particular, failures can result in disproportionate ownership
of groups which may cause a byzantine fault to occur.

@@

\subsection{Effects of Node failures on group and signature characteristics}
To evaluate the possible effects of node failure on group and signature characteristics, we use the
multi-run study. We then observe trends in the specific parameters discussed below.

\subsection{Effects of stake distributions on group and signature characteristics}

@@

\begin{figure*}[h]
    \onecolumn
    \centering
    \includegraphics[width=\linewidth]{steady_state_behavior.pdf}
    \caption{Emergence of Steady State Behavior}
    \label{fig:steady_state}
\end{figure*}

\newpage
\begin{table}[htbp]
    \caption{Node Agent}
    \begin{center}
    \begin{tabular}{|c|c|}
    \cline{1-2} 
    \textbf{Key Attributes}&{\textbf{Node Agent}} \\
    \cline{1-2} 
    \hline
    Connection Delay & Delay between when a node is created and when it can join the network \\
    Ticket List & List of random numbers used to pick the node for participation in a group\\
    Connection Failure Percent & Likelihood of disconnecting from the network\\
    Death Percent & Likelihood of going offline and never re-connecting\\
    Malicousness & determines if a node is considered malicous based on if the operator is malicious\\
    Operator  & the entity that runs this node\\
    \hline
    \textbf{ }&\textbf{Group Agent} \\
    \hline
    Members & list of nodes that are members of the group. Nodes can repeat \\
    Expiry & number of blocks before group expires\\
    Malicious Percent & percentage of the groups members that are malicious\\
    Offline Percent & percentage of the groups members that are offline\\
    DKG Delay & User set delay simulating the distributed key generation process during group creation\\
    \hline
    \textbf{ }&\textbf{Signature Agent} \\
    \hline
    Group & list of nodes that are members of the group. Nodes can repeat \\
    Expiry & number of blocks before group expires\\
    Delay &  user specified time between being triggered and being published on chain\\
    Offline Percent & percentage of the groups members that are offline at the time of the signature\\
    Lynchpin operator percent & percent of the group owned by a single operator\\
    \hline
    \multicolumn{2}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
    \end{tabular}
    \label{table}
    \end{center}
    \end{table}

>>>>

\subsection{How could node failures and group sizes affect system behavior?}
Nodes may go offline or fail entireley. Since their participation in groups is critical to the 
success of the threshold relay, it is important to understand the impact of various levels
of failure on group characteristics. In particular, failures can result in disproportionate ownership
of groups which may cause a byzantine fault to occur.

@@

\subsection{Effects of Node failures, Group Size and Stake Distributions}
To evaluate the possible effects of node failure and stake distributions on group and signature 
characteristics, we use the multi-run study. We then observe trends in the specific parameters 
discussed below. We also run each multi run study for each of the three distribitions to study 
the correlation between the observed trends and the type of stake distribution.

    Using the \textit{linear distribution:}

        \begin{table}[htbp]
            \caption{Lynchpinned Signatures}
            \begin{center}
            \begin{tabular}{|c|c|c|c|}
            \hline
            \textbf{Failure}&\multicolumn{3}{|c|}{\textbf{Group Size}} \\
            \cline{2-4} 
            \textbf{Percent} & \textbf{\textit{50}}& \textbf{\textit{100}}& \textbf{\textit{150}} \\
            \hline
            5 &  0.006065 &  0.000000 &  0.000000 \\
            \hline
            10 &  0.071656 &  0.009276 &  0.003985 \\
            \hline
            20 &  0.399020 &  0.262837 &  0.177465 \\
            \hline
            \end{tabular}
            \label{lynchpinned_table1}
            \end{center}
        \end{table}

        \begin{table}[htbp]
            \caption{Compromised Groups}
            \begin{center}
            \begin{tabular}{|c|c|c|c|}
            \hline
            \textbf{Failure}&\multicolumn{3}{|c|}{\textbf{Group Size}} \\
            \cline{2-4} 
            \textbf{Percent} & \textbf{\textit{50}}& \textbf{\textit{100}}& \textbf{\textit{150}} \\
            \hline
            5 &  0.590035 &  0.435403 &  0.407054 \\
            \hline
            10 &  0.428957 &  0.710509 &  0.536904 \\
            \hline
            20 &  0.557832 &  0.591663 &  0.555565 \\
            \hline
            \end{tabular}
            \label{compromised_table1}
            \end{center}
        \end{table}

        \begin{table}[htbp]
            \caption{Failed Signatures}
            \begin{center}
            \begin{tabular}{|c|c|c|c|}
            \hline
            \textbf{Failure}&\multicolumn{3}{|c|}{\textbf{Group Size}} \\
            \cline{2-4} 
            \textbf{Percent} & \textbf{\textit{50}}& \textbf{\textit{100}}& \textbf{\textit{150}} \\
            \hline
            5 &  0.0 &  0.0 &  0.0 \\
            \hline
            10 &  0.0 &  0.0 &  0.0 \\
            \hline
            20 &  0.0 &  0.0 &  0.0 \\
            \hline
            \end{tabular}
            \label{failed_table1}
            \end{center}
        \end{table}

        Using the \textit{Ethereum distribution:}

@@

\newpage
\begin{figure*}[h]
    \onecolumn
    \centering
    \includegraphics[width=\linewidth]{steady_state_behavior.pdf}
    \caption{Emergence of Steady State Behavior}
    \label{fig:steady_state}
\end{figure*}

\newpage
\begin{table}[htbp]
    \caption{Node Agent}
    \begin{center}
    \begin{tabular}{|c|c|}
    \cline{1-2} 
    \textbf{Key Attributes}&{\textbf{Node Agent}} \\
    \cline{1-2} 
    \hline
    Connection Delay & Delay between when a node is created and when it can join the network \\
    Ticket List & List of random numbers used to pick the node for participation in a group\\
    Connection Failure Percent & Likelihood of disconnecting from the network\\
    Death Percent & Likelihood of going offline and never re-connecting\\
    Malicousness & determines if a node is considered malicous based on if the operator is malicious\\
    Operator  & the entity that runs this node\\
    \hline
    \textbf{ }&\textbf{Group Agent} \\
    \hline
    Members & list of nodes that are members of the group. Nodes can repeat \\
    Expiry & number of blocks before group expires\\
    Malicious Percent & percentage of the groups members that are malicious\\
    Offline Percent & percentage of the groups members that are offline\\
    DKG Delay & User set delay simulating the distributed key generation process during group creation\\
    \hline
    \textbf{ }&\textbf{Signature Agent} \\
    \hline
    Group & list of nodes that are members of the group. Nodes can repeat \\
    Expiry & number of blocks before group expires\\
    Delay &  user specified time between being triggered and being published on chain\\
    Offline Percent & percentage of the groups members that are offline at the time of the signature\\
    Lynchpin operator percent & percent of the group owned by a single operator\\
    \hline
    \multicolumn{2}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
    \end{tabular}
    \label{agent_table}
    \end{center}
    \end{table}
